\documentclass[letterpaper,10pt,twoside,twocolumn,openany]{book}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{dnd}
\usepackage{dndcharacter}
\usepackage{tabularx}

\begin{document}

\section{Maruf ibn Mansur}

Human Druid 2 (\textit{Lawful Neutral})

\subsection{Skills/Saves}
\saves[
    STR=\stat{9},
    DEX=\stat{15},
    CON=\stat{16},
    INT=\stat{10},
    WIS=\stat{16},
    CHA=\stat{10},
    IPROF=1,
    WPROF=1,
    NATURE=1,
    SURVIVAL=1,
    INSIGHT=1,
    PERCEPTION=1,
]

\subsection{Combat}
\begin{tabularx}{\columnwidth}{rlrl}
  \textbf{AC:}          & 15          & \textbf{Proficiency:} & +2\\
  \textbf{Initiative:}  & +2          & \textbf{Speed:}       & 30 \\
  \textbf{Hit Dice:}    & 2d8 \Circle & \textbf{Hit Points:}  & \parbox[l][1em][c]{1em}{19} / 19 \\
  \textbf{Death Saves}  & \Circle \Circle \Circle \\
                        & \Circle \Circle \Circle
\end{tabularx}

\subsection{Weapons}
\begingroup
  \begin{monsteraction}[Scimitar]
    \textit{Melee Weapon Attack:} +2 to hit, reach 5ft., Single Target. \textit{Hit:} \dice{1d6+2} slashing damage.
  \end{monsteraction}

  \begin{monsteraction}[Dagger]
    \textit{Ranged or Melee Weapon Attack:} +2 to hit, reach 5ft., range 20/60 feet, Single Target. \textit{Hit:} \dice{1d4+2} piercing damage.
  \end{monsteraction}
\endgroup%

\subsection{Proficiencies}
Light armor, medium armor, shields, clubs, daggers, darts, javelins, maces, quarterstaffs, scimitars, sickles, slings, spears, herbalism kit, Quanun (Reskinned Dulcimer)

\subsection{Equipment}
Wooden Shield, Scimitar, leather armor, druidic focus, an explorer's pack, one set of travellers clothes, Quanun (Reskined Dulcimer), poorly made maps from Zakhara that depict the Sword Coast, my father's signet ring (10gp), coin pouch

\subsection{Treasure}
\begin{tabular}{ll}
PP \rule{.5in}{.2pt} &Miscellaneous:\\
GP 5 &\rule{2.2in}{.2pt}\\
EP \rule{.5in}{.2pt} &\rule{2.2in}{.2pt}\\
SP \rule{.5in}{.2pt} &\rule{2.2in}{.2pt}\\
CP \rule{.5in}{.2pt} &\rule{2.2in}{.2pt}\\
\end{tabular}

\subsection{Spells}
\subsubsection{Cantrips}
\textit{Poison Spray}, \textit{Druidcraft}
\subsubsection{Level 1 --- \CIRCLE \CIRCLE \Circle}
\begin{tabularx}{\columnwidth}{cXcX}
  \Circle & \textit{Animal Friendship}       & \Circle & \textit{Charm Person} \\
  \CIRCLE & \textit{Create or Destroy Water} & \CIRCLE & \textit{Cure Wounds} \\
  \Circle & \textit{Detect Magic}            & \CIRCLE & \textit{Entangle} \\
  \Circle & \textit{Faerie Fire}             & \Circle & \textit{Fog Cloud} \\
  \Circle & \textit{Goodberry}               & \Circle & \textit{Healing Word} \\
  \Circle & \textit{Jump}                    & \Circle & \textit{Longstrider} \\
  \Circle & \textit{Purify Food and Water}   & \Circle & \textit{Speak with Animals} \\
  \CIRCLE & \textit{Thunderwave}
\end{tabularx}

\subsection{Special}
\begin{specialability}[Druidic]
  I know Druidic, the secret language of druids. I can speak the language and use it to leave hidden messages. I and others who know this language automatically spot such a message. Others spot the message’s presence with a successful DC 15 Wisdom (Perception) check but can ’t decipher it without magic.
\end{specialability}

\begin{specialability}[All Eyes on You]
  My accent, mannerisms, figures of speech, and even my appearance all mark me as foreign. Curious glances are directed my way wherever I go, which can be a nuisance, but I also gain the friendly interest of scholars and others intrigued by far off lands, to say nothing of every day folk who are eager to hear stories of my homeland.

  I can parley this attention into access to people and places I might not otherwise have, for me and my travelling companions. Noble lords, scholars, and merchant princes, to name a few, might be interested in hearing about my distant homeland and people.
\end{specialability}

\begin{specialability}[Circle of the Moon]
  Changeable as the moon, I might prowl as a great cat one night, soar over the treetops as an eagle the next day, and crash through the undergrowth
  in bear form to drive off a trespassing monster. The wild is in my blood.
\end{specialability}

\begin{specialability}[Combat Wild Shape]
  I have the ability to use Wild Shape on my turn as a bonus action, rather than as an action.

  Additionally, while I am transformed by Wild Shape, I can use a bonus action to expend one spell slot to regain 1d8 hit points per level of the spell slot expended.
\end{specialability}

\begin{specialability}[Circle Forms]
  The rites of my circle grant me the ability to transform into more dangerous animal forms. I can use my Wild Shape to transform into a beast with a challenge rating as high as 1.
\end{specialability}


\begin{specialability}[Wild Shape]
  I can use my action to magically assume the shape of a beast that I have seen before. I can use this feature twice. I regain expended uses when I finish a short or long rest.

  My beast form is limited to a maximum of CR 1 with no flying or swimming speed.

  I can stay in a beast shape for a number of hours equal to half my druid level (rounded down). I then revert to my normal form unless I expend another use of this feature. I can revert to my normal form earlier by using a bonus action on my turn. I automatically revert if I fall unconscious, drop to 0 hit points, or die.

  While I am transformed, the following rules apply:
  \begin{itemize}
    \item My game statistics are replaced by the statistics of the beast, but I retain my alignment, personality, and Intelligence, Wisdom, and Charisma scores. I also retain all of my skill and saving throw proficiencies, in addition to gaining those of the creature. If the creature has the same proficiency as me and the bonus in its stat block is higher than mine, use the creature’s bonus instead of mine. If the creature has any legendary or lair actions, I can't use them.

    \item When I transform, I assume the beast’s hit points and Hit Dice. When I revert to my normal form, I return to the number of hit points I had before I transformed. However, if I revert as a result of dropping to 0 hit points, any excess damage carries over to my normal form. As long as the excess damage doesn’t reduce my normal form to 0 hit points, I'm not knocked unconscious.

    \item I can’t cast spells, and my ability to speak or take any action that requires hands is limited to the capabilities of my beast form. Transforming doesn’t break my concentration on a spell I've already cast, however, or prevent me from taking actions that are part of a spell, such as call lightning, that i've already cast.

    \item I retain the benefit of any features from my class, race, or other source and can use them if the new form is physically capable of doing so. However, I can’t use any of my special senses, such as darkvision, unless my new form also has that sense.

    \item I choose whether my equipment falls to the ground in my space, merges into my new form, or is worn by it. Worn equipment functions as normal, but the DM decides whether it is practical for the new form to wear a piece of equipment, based on the creature’s shape and size. My equipment doesn’t change size or shape to match the new form, and any equipment that the new form can’t wear must either fall to the ground or merge with it. Equipment that merges with the form has no effect until I leave the form.
  \end{itemize}
\end{specialability}

\subsection{Personality}

\textbf{Background: Far Traveller} I am from the far off land of Zakhara. My family have ranged far and wide as traders and travellers. I once sought a life of ascietism, separate from the wealth that my father pursued, but his deathbed confession has driven me to try to right wrongs he committed far from home.

\textbf{Personality Trait:} I have my own ideas about what is and is not food and I find the eating habits of those around me fascinating, confusing, and sometimes revolting.

\textbf{Ideals: Suspicious} Everything is new, but I have a thirst to learn.

\textbf{Bonds:} On his deathbed, my father confessed that he had become involved with a group called the Cult of the Dragon. They paid him to smuggle goods across the Sword Coast. Wracked by guilt, he begged me to investigate the cult and undo the evil he may have helped foster. He urged me to begin my search in a town called Greenest.

\textbf{Flaws:} I have a weakness for the exotic beauty of the people of these lands.

\end{document}
